---
title: "Health Equity Vulnerable Loc // Max Coverage"
author: "Enterprise Analytics"
date: "`r paste0('Last Updated: ', format(Sys.time(), '%d %B, %Y')) `"
keywords: 
  - Office
output: 
  eaverse::ea_report:
    analyst: 
    - "P. Walker"
    email: "philip.walker@conehealth.com"
    draft: false
    code_folding: "show" # one of "show", "hide", or "none"
    code_download: FALSE # TRUE to allow the Rmd to be downloaded or FALSE
# knit: eaverse::knit_ea_letter
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE) #echo = FALSE, 
knitr::opts_chunk$set(fig.align = 'center')
library(tidyverse)
library(kableExtra)
library(eaverse)
library(sf)
library(tigris)
library(leaflet)
library(leaflet.extras)
library(maxcovr)
# To Turn off Scientific Notation Use this.
options(scipen = 999)

# This cleans up numbers to add decimal places
knitr::knit_hooks$set(inline = clean_numbers,
                      dropdown = knit_dropdown,
                      chunk = ea_hooks)
```

# Executive Summary {.tabset .tabset-pills}

## Top line review

```{block, summary = TRUE, echo = TRUE}
__Challenge:__ Our most vulnerable population in Greensboro has a decreased access to care not only due their challenging life situations but also due to the limited available resources within a reasonable distance. This leads to a decreased likelihood of utilizing preventative care and often worse health outcomes for this already at risk population.

__Goal:__ To improve healthcare access to our underserved communities in Greensboro by increasing physical office options.

__Define Success:__  We will have successfully provided recommendations if:  

1.	We have defined the population of interest   
    *	Utilizing CDC’s Social Vulnerability Index to determine which block groups within Greensboro we should focus our analysis efforts on. (highly vulnerable > 0.8)  
2.	Access success criteria: Is the office location within reasonable walking distance?   
    *	Average Euclidian distance < 0.75 mile   
    *	Covering 60% within 0.75 mile    
3.	Provided fewest number of additional locations to meet the above items  
  

__Actions we can take:__  

* Use the model as a tool to help organize our focus on potential locations for new office locations.
* Compare recommendations to current non-Cone locations, these could be opportunties for partnerships.  


```


## Data used

```{block, summary = TRUE, echo = TRUE}

The final result combines multiple data sources. Below are the different data sources used.  

* Rebuilt CDC Social Vulnerability Index (SVI) on block group level
* 2020 projected population on the block level
* All Cone patients with 1+ encounter(s) (and has a geocoded address) from 2018 to now .  
* Office Locations from Strategy and Practice Provider tables. 
    * including Cone offices and Non-Cone offices
* GSO Open Data portal for parcel data  
* GTA Bus Stops

```


## Methods 

```{block, summary = TRUE, echo = TRUE}

__Current office locations__

* Gather office location data and consolidate from:
  *	Strategy team
  * THN Practice Provider locations 
* Using office locations that CHMG/CHC and have specialties of Family Med, Internists, Pediatrician, OBGYN


__Characterize vulnerability range__  

* Using American Community Survey to rebuild the CDC’s Social Vulnerability Index at a more refined level (from tract -> block group)
* Define “most vulnerable” as communities with an index __> 80%__ (80th percentile)


__Characterize current coverage rate__  

* Using highly vulnerable communities to filter down patient encounter information
* Calculated coverage rate as amount of highly vulnerable patients within a 0.75 mi radius of the nearest Cone office location.


__Capture current parcel data__    

* Capture Zone and Land Class types data from GSO Open Data portal    
    *	Filter down to Office/Retail/Commercial/Industrial related land class and zones  


__Propose locations__ 

* Combining all datasets above  
* Utilize a maximal coverage model to:  
    1. Assess current coverage 
    1. Provide a range of recommendations from current parcels that fit the zoning requirements. 

```


## Assumptions made

```{block, summary = TRUE, echo = TRUE}

__Items not included in analysis:__ 

*	Recommendations of office characteristics     
    * Services to provide, hours to be open, staffing required, community/demographic fit    
*	Recommendations for outreach efforts    
    *	Effectiveness of fliers/ads, community coordination, behavior change   
    * Changing perception of current office locations to improve utilization  
*	Characterization of potential costs   
    *	Start-up + operations costs  
    *	Expected reimbursement   
*	Address-level office recommendations  
*	Recommendations does not currently include transportation access  
*	Assessment of other health system patient coverage  
    *	In terms of patient information, we also don’t have visibility to the people we aren’t currently serving.  


```



# Build Model {.tabset .tabset-pills}

## Read in Data

Setting variables of interest
```{r, echo=TRUE}

HighVulPCT <- 0.8
radius <- 0.75
CoverDist <- radius*1609.34

```

Loading in data built and cleaned in prior steps and them combing them all.
```{r, echo=TRUE}
load(file = here::here("data","CurrentOffices.rda")) # Current offices from Strategy and THN Practice Providers
load(file = here::here("data","GSO_bus_stops.rda")) # for visuals, from GSO GSI team
load(file = here::here("data","GSO_SVI.rda")) # Rebuilt SVI on block group, filtered down to GSO tracts
load(file = here::here("data-raw", "LocationsGEO.rda")) #extracted all zoned offices, etc

OfficeGSO <- 
  LocationsGEO %>%  
  mutate(y = as.numeric(y),
         x = as.numeric(x)) %>% 
  st_as_sf(coords = c('x', 'y'), crs = st_crs(GSO_SVI)) %>% 
  ungroup()

SVI <- 
  GSO_SVI %>% 
  select(GEOID, NAME, PCT, geometry) %>% 
  separate(NAME, into = c("Block Group", "Tract", "County", "State"), sep = ", ")

GSO_bus_stops <- 
  GSO_bus_stops %>%  
  mutate(y = as.numeric(stop_lat),
         x = as.numeric(stop_lon)) %>% 
  st_as_sf(coords = c('x', 'y'), crs = st_crs(GSO_SVI))


```

```{r}
OfficeXY <- 
  OfficeGSO %>% 
  st_coordinates() %>% 
  as_tibble() %>%
  mutate(id = row_number())
  

Office <- 
  OfficeGSO %>% 
  mutate(id = row_number()) %>% 
  left_join(.,
            OfficeXY, by = c("id")) %>% 
  select(-id) %>% 
  rename(long = X,
         lat = Y)

rm(OfficeXY, OfficeGSO)
```



Setting highly vulnerable from the SVI index for the block group

```{r, echo = T}
HighVul_Loc <- 
  SVI %>% 
  filter(PCT >= HighVulPCT)

```

```{r, eval=F}
HV_buffer <-
  SVI %>%
  filter(lengths(st_touches(., HighVul_Loc)) > 0)

```



Reading in patient population
```{r, echo=TRUE}
load(file = here::here("data-raw", "RecentPatients_Geo.rda")) # Patients with any encounter (and an address) from 2018 to now

PatientsInHighVul <- 
  Cone_Loca %>% 
  filter(!FIPS == "") %>% 
  mutate(Y = as.numeric(Y),
         X = as.numeric(X)) %>% 
  st_as_sf(coords = c('X', 'Y'), crs = st_crs(GSO_SVI)) %>% 
  st_intersection(., HighVul_Loc %>% select(geometry))

rm(Cone_Loca)

```

```{r}
PatXY <- PatientsInHighVul %>% 
  st_coordinates() %>% 
  as_tibble() %>%
  mutate(id = row_number())
  

Pats <- 
  PatientsInHighVul %>% 
  mutate(id = row_number()) %>% 
  left_join(.,
            PatXY, by = c("id")) %>% 
  select(-id) %>% 
  rename(long = X,
         lat = Y)

rm(PatXY, PatientsInHighVul)
   
```


```{r}
# Reading in census population proxy
load(file = here::here("data-raw", "guil_cent_rep.rda"))

CensusPop <- 
  guil_cent_rep %>% 
  st_drop_geometry() %>% 
  st_as_sf(coords = c('lon','lat'), crs = st_crs(GSO_SVI)) %>% 
  st_intersection(., HighVul_Loc %>% select(geometry))

rm(guil_cent_rep)

```

```{r}
PopXY <- CensusPop %>% 
  st_coordinates() %>% 
  as_tibble() %>%
  mutate(id = row_number())
  

Pop <- 
  CensusPop %>% 
  mutate(id = row_number()) %>% 
  left_join(.,
            PopXY, by = c("id")) %>% 
  select(-id) %>% 
  rename(long = X,
         lat = Y)

rm(CensusPop, PopXY)

```



## Maxium Coverage {.active}



```{r}
# Current Coverage
ConeLoc_df <- 
  CurrentOffices %>% 
  filter(Affli_Group == "Cone") %>% 
  mutate(id = row_number())

Pats_df <- 
  Pats %>% 
  st_drop_geometry()

Pop_df <- 
  Pop %>% 
  st_drop_geometry()

Office_df <- 
  Office %>% 
  st_drop_geometry()


```

```{r, fig.width=12, out.width="100%"}

PatientCov <- bind_rows(
  coverage(ConeLoc_df, 
         Pats_df,
         distance_cutoff = CoverDist) %>% 
  mutate(Type = "Patient Coverage"),
  coverage(ConeLoc_df, 
         Pop_df,
         distance_cutoff = CoverDist) %>% 
  mutate(Type = "Census Population Coverage")
) 

# PatientCov %>% 
#   kable()

library(gt)

PatientCov %>% 
  relocate(Type, .before = distance_within) %>% 
  select(-distance_within) %>% 
  gt() %>% 
  tab_header(
    title = md("**Coverage Summary**"),
    subtitle = md("Comparing Cone Patients vs Population on block level")
  ) %>% 
  fmt_number(
    columns = vars(n_cov, n_not_cov, dist_avg, dist_sd),
    suffixing = F,
    decimals=0
  ) %>% 
  fmt_percent(
    columns = vars(prop_cov, prop_not_cov),
    decimals = 1
  )


```


This contains useful summary information:  

* distance_within - this is the distance used to determine coverage   
* n_cov - this is the number of events that are covered  
* n_not_cov - the number of events not covered  
* pct_cov - the proportion of events covered  
* pct_not_cov - the proportion of events not covered  
* dist_avg - the average distance from the rows to the nearest facility or user  
* dist_avg - the standard deviation of the distance from the rows to the nearest facility or user.  


This tells us that out of all the patients living in highly vulnerable locations, __`r  scales::percent(PatientCov$prop_cov[1], accuracy= 0.1)`__ of them live within __`r radius` miles__) of a Cone Office, with the mean distance to a current office location is __2335m (~ 1.5 miles)__.


```{r}
mc_1 <- max_coverage(existing_facility = ConeLoc_df,
                      proposed_facility = Office_df,
                      user = Pats_df,
                      n_added = 1,
                      distance_cutoff = CoverDist)

# mc_2 <- max_coverage(existing_facility = ConeLoc_df,
#                       proposed_facility = Office_df,
#                       user = Pats_df,
#                       n_added = 2,
#                       distance_cutoff = CoverDist)

mc_3 <- max_coverage(existing_facility = ConeLoc_df,
                      proposed_facility = Office_df,
                      user = Pats_df,
                      n_added = 3,
                      distance_cutoff = CoverDist)

# mc_4 <- max_coverage(existing_facility = ConeLoc_df,
#                       proposed_facility = Office_df,
#                       user = Pats_df,
#                       n_added = 4,
#                       distance_cutoff = CoverDist)

mc_5 <- max_coverage(existing_facility = ConeLoc_df,
                      proposed_facility = Office_df,
                      user = Pats_df,
                      n_added = 5,
                      distance_cutoff = CoverDist)

```


```{r, eval=F}
mc_1$summary[[1]]
mc_3$summary[[1]]
mc_5$summary[[1]]


```

```{r, fig.height=6, fig.width=12, out.width="100%", eval=TRUE}

CompareRuns  <- 
  bind_rows(mc_1$summary[[1]], mc_3$summary[[1]], mc_5$summary[[1]]) %>%
  unique() %>% 
  ungroup() 
  
CompareRuns %>% 
ggplot(aes(n_added, pct_cov))+
    geom_point()+
    geom_line()+
    geom_hline(aes(yintercept = 0.6), linetype = "dashed", color="black") +
    scale_y_continuous(labels = scales::percent_format())+
    labs(y = "Percent Coverage", x = "Amount of Sites Added",
         title = "Projected Patient Coverage by Amount of New Sites")


```


# Results


```{r}
popupPOP <- paste("Name: ", GSO_SVI$NAME,
                  "<br/>",
                  "Population: ", scales::comma(GSO_SVI$POP),
                  "<br/>",
                  "Social Vulnerability Index: ", scales::percent(GSO_SVI$PCT, accuracy = 1),
                  sep="") %>%
  lapply(htmltools::HTML)


SVIpal <- colorNumeric(
  palette = "BuPu",
  domain = GSO_SVI$PCT
)

```


```{r}
NonCone_Loc <- 
  CurrentOffices %>% filter(!Affli_Group == "Cone")

Cone_only <-
  CurrentOffices %>% filter(Affli_Group == "Cone")
```



```{r, fig.height=8, fig.width=6, out.width="100%", eval=TRUE}

leaflet() %>%
addPolygons(data = GSO_SVI,
    popup = ~ popupPOP,
    group = "SVI",
    fillColor = ~ SVIpal(PCT),
    color = "#444444",
    weight = 1,
    smoothFactor = 0.5,
    opacity = 1.0,
    fillOpacity = 0.5,
    highlightOptions = highlightOptions(
      color = "white",
      weight = 2,
      bringToFront = TRUE
    ),
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"
    )) %>% 
  addCircles(data = mc_5$facility_selected[[1]], 
               radius = CoverDist,
               fill = NULL,
               opacity = 0.99,
               weight = 2,
               color = "green",
               dashArray = "1,5",
             group = "Suggested Sites") %>%
  addCircles(data = Cone_only,
               radius = CoverDist, #1 mile (in meters)
               stroke = TRUE,
               fill = NULL,
               opacity = 0.99,
               weight = 2,
               color = "coral",
             group = "Cone Locations",
             popup = Cone_only$GroupedEth) %>%
    addCircles(data = NonCone_Loc,
               radius = CoverDist, #1 mile (in meters)
               stroke = TRUE,
               fill = NULL,
               opacity = 0.99,
               weight = 2,
               color = "purple",
             group = "Non-Cone Locations",
             popup = NonCone_Loc$GroupedEth) %>%
    addCircleMarkers(data = Pats_df, 
                     radius = 0.7,
                     color = "steelblue",
                     group = "Patients") %>%
     addCircleMarkers(data = Office_df, 
                     radius = 1,
                     color = "green",
                    popup = Office_df$ZONING,
                    group = "Zoned Parcels") %>%
     addCircles(data = GSO_bus_stops, 
                     radius = 0.75,
                     group = "GTA stops",
                     color = "black") %>%
       addCircles(data = Pop_df, 
                     radius = 0.75,
                     group = "Census Population",
                     color = "lightblue") %>%
    addProviderTiles(provider= "CartoDB.Positron") %>%  #"Esri.WorldStreetMap") %>%
    setView(lng = median(Pats$long),
            lat = median(Pats$lat),
            zoom = 12) %>% 
  addLayersControl(
    overlayGroups = c("SVI","Suggested Sites", "Cone Locations", "Non-Cone Locations", "Patients", 
                      "Census Population", "Zoned Parcels", "GTA stops"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>% 
  addFullscreenControl() %>% 
  addResetMapButton() %>% 
  addLegend("bottomleft", colors= c("coral", "purple" ,"steelblue", "green", "black"), labels=c("Cone Offices", "Non-Cone Offices", "Patients", "Parcels", "GTA Stops"), title="") %>% 
  hideGroup(c("GTA stops", "SVI", "Zoned Parcels", "Census Population", "Non-Cone Locations")) %>% 
    setMaxBounds(lng1 = min(CurrentOffices$long),
               lat1 = min(CurrentOffices$lat),
               lng2 = max(CurrentOffices$long),
               lat2 = max(CurrentOffices$lat)) %>% 
  addScaleBar(position = c("bottomleft"), options = scaleBarOptions())
  # leafem::addLogo(
  #   img = "img/conelogo.png", src = "local",
  #   position = c("bottomright"),
  #   offset.x = 0, offset.y = 10,
  #   width = 180, height = 40) %>% 

```



```{r}
save(GSO_SVI, CurrentOffices,Pats_df,Office_df,GSO_bus_stops,Pop_df, 
     file = here::here("output", "AllFiles.rda"))

```








